taxview
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE
)
```

[![Project Status: Suspended – Initial development has started, but there has not yet been a stable, usable release; work has been stopped for the time being but the author(s) intend on resuming work.](https://www.repostatus.org/badges/latest/suspended.svg)](https://www.repostatus.org/#suspended)
[![R-check](https://github.com/ropensci/taxview/workflows/R-check/badge.svg)](https://github.com/ropensci/taxview/actions)

Summarise and visualize data sets taxonomically

The proposed workflow with `taxview`:

- input:
  - data.frame with data, indicate which column has names or ids
  - vector/list of names or ids (not associated with data)
- gather taxonomic classification data for each taxon
- from previously collected data, compute summary statistics/etc.
- visualize data among taxonomic groups, etc.

## install

```{r eval=FALSE}
remotes::install_github("ropensci/taxview")
```

```{r}
library(taxview)
```

## use

get some data

```{r}
x <- system.file("examples/plant_spp.csv", package = "taxview")
```

prepare data: clean, etc.

```{r}
dat <- tibble::as_tibble(
 data.table::fread(x, stringsAsFactors = FALSE, 
   data.table = FALSE))
out <- tv_prep_ids(x, ids = dat$id, db = "ncbi")
```

Prepare summary. The output of `tv_summarise()` is an S3 class, with a summary of the groupings.

```{r}
res <- tv_summarise(out)
res
```

The `$summary` slot has the number of taxa in the dataset

```{r}
res$summary
```

The `$by_rank` slot has the breakdown of taxa within each rank category, as a count and percentage.

```{r}
res$by_rank
```

The `$by_rank_name` slot has the breakdown of taxa ...

```{r}
res$by_rank_name
```

The `$by_within_rank` slot has the breakdown of number of records within each taxon within each rank grouping.

```{r}
res$by_within_rank[1:2]
```

visualize (NOT WORKING YET)

```{r eval=FALSE}
tv_viz(res)
```

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/taxview/issues).
* License: MIT
* Get citation information for `taxview` in R doing `citation(package = 'taxview')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
