taxview
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE
)
```

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![Build Status](https://travis-ci.org/ropensci/taxview.svg?branch=master)](https://travis-ci.org/ropensci/taxview)

Summarise and visualize data sets from with respect to taxonomy

## install

```{r eval=FALSE}
devtools::install_github("ropensci/taxview")
```

```{r}
library(taxview)
```

## use

get some data

```{r}
x <- system.file("examples/plant_spp.csv", package = "taxview")
```

prepare data: clean, etc.

```{r}
dat <- tibble::as_tibble(
 data.table::fread(x, stringsAsFactors = FALSE, 
   data.table = FALSE))
head(dat)
dat_clean <- tv_clean_ids(x, ids = dat$id, db = "ncbi")
head(dat_clean)
```

prepare summary

```{r}
(sumdat <- tv_summarise(dat_clean))
```

visualize (NOT WORKING YET)

```{r eval=FALSE}
tv_viz(sumdat)
```

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/taxview/issues).
* License: MIT
* Get citation information for `taxview` in R doing `citation(package = 'taxview')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
